\documentclass[conference]{IEEEtran}
\usepackage{times}

\usepackage{amsmath,amssymb}

%  For drawing Bayesian networks
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{tikz-cd}

% numbers option provides compact numerical references in the text. 
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

\pdfinfo{
   /Author (Henry O. Jacobs)
   /Title  (Robots: Our new overlords)
   /CreationDate (D:20101201120000)
   /Subject (Robots)
   /Keywords (Robots;Overlords)
}

\begin{document}

% paper title
\title{Realtime Probabilistic Pedestrian Forecasting}

% You will get a Paper-ID when submitting a pdf file to the conference system
\author{Author Names Omitted for Anonymous Review. Paper-ID [add your ID here]}

%\author{\authorblockN{Michael Shell}
%\authorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: mshell@ece.gatech.edu}
%\and
%\authorblockN{Homer Simpson}
%\authorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\authorblockN{James Kirk\\ and Montgomery Scott}
%\authorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}


% avoiding spaces at the end of the author lines is not a problem with
% conference papers because we don't use \thanks or \IEEEmembership


% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\authorblockN{Michael Shell\authorrefmark{1},
%Homer Simpson\authorrefmark{2},
%James Kirk\authorrefmark{3}, 
%Montgomery Scott\authorrefmark{3} and
%Eldon Tyrell\authorrefmark{4}}
%\authorblockA{\authorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: mshell@ece.gatech.edu}
%\authorblockA{\authorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\authorblockA{\authorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\authorblockA{\authorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}


\maketitle

\begin{abstract}
The abstract goes here.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}

\section{Model}
%Describe scenario in english.
Our goal is to generate a time-dependent pdf over space, $\rho(x,t)$, which predicts the true location of an agent in the future.
The input to the algorithm is a noisy measurement of position and velocity in the present, as well as an archive of past trajectories that have run through the scene.

At time $t=0$, we obtain a noisy reading of position, $\hat{x}_0 \in \mathbb{R}^2$.
We assume that our measurements come from Gaussian noise about the true location $x_0 \in \mathbb{R}^2$,
so that $\Pr(\hat{x}_0 \mid x_0 ) = (2\pi \sigma_x^2)^{-1} \exp( - \| \hat{x}_0 - x_0 \|^2 / (2 \sigma_x^2) )$.
Therefore, at time $0$, we have $\rho(x,0) = \Pr(\hat{x}_0 \mid x_0 )$.

In order to solve $\rho(x,t)$ at later times, we need to assume a dynamical model.
In our model, agents move through space under the dynamics of the form
$$
	\frac{dx}{dt}(t) = s \cdot X_k(x(t))
$$
where $X_k$ is a director-field from a finite collection $\{X_1, \dots, X_n\}$, and $s \in \mathbb{R}$.
It is assumed that $k$ and $s$ are both constant in time.
Under this model, if you know $x_0$ precisely, and you know $k$ and $s$, then you know the full curve $x(t)$ for all time.
Generally, we do not know $x_0$ or $k$ or $s$ precisely.
However, we can consider the Bayesian network
\begin{center}
\begin{tikzpicture}[thick, var/.style={circle,draw,thin,rounded corners,shade,top color=blue!50,minimum size = 4mm}]
	\node[var] (s) {$s$};
	\node[var] (k) [right=of s]{$k$};
	\node[var] (x) [right=of k] {$x_0$};
	\node[var] (v) [below=of x] {$v$};
	\node[var] (x_hat) [right=of x] {$\hat{x}_0$};
	\node[var] (v_hat) [right=of v] {$\hat{v}_0$};
	\node[var] (rho) [above=of x] {$\rho(x,t)$};
	
	\draw[->] (s.east) to (rho.west);
	\draw[->] (s.east) to (v.west);
	\draw[->] (k.north east) to (rho.south west);
	\draw[->] (k.east) to (x.west);
	\draw[->] (k.south east) to (v.north west);
	\draw[->] (x.north) to (rho.south);
	\draw[->] (x.south) to (v.north);
	\draw[->] (x.east) to (x_hat.west);
	\draw[->] (v.east) to (v_hat.west);
\end{tikzpicture}
\end{center}
Which allows us to derive $\rho(x,t)$ by appropriately marginalizing over the full joint probability $\Pr(x(t), x_0, v_0, \hat{x}_0, \hat{v}_0, k, s)$.

\subsection{Inverse optimal control}
This section is optional.  Describe how director-fields are solutions of optimization problems.

\section{Learning}
  Describe how $\Pr(x \mid k)$, the director-fields, and $\sigma_x$ are learned without using math.
  Math will be relegated to the appendix.
  
\section{Results}
 Precision, accuracy, etc.

\section{RSS citations}

Please make sure to include \verb!natbib.sty! and to use the
\verb!plainnat.bst! bibliography style. \verb!natbib! provides additional
citation commands, most usefully \verb!\citet!. For example, rather than the
awkward construction 

{\small
\begin{verbatim}
\cite{kalman1960new} demonstrated...
\end{verbatim}
}

\noindent
rendered as ``\cite{kalman1960new} demonstrated...,''
or the
inconvenient 

{\small
\begin{verbatim}
Kalman \cite{kalman1960new} 
demonstrated...
\end{verbatim}
}

\noindent
rendered as 
``Kalman \cite{kalman1960new} demonstrated...'', 
one can
write 

{\small
\begin{verbatim}
\citet{kalman1960new} demonstrated... 
\end{verbatim}
}
\noindent
which renders as ``\citet{kalman1960new} demonstrated...'' and is 
both easy to write and much easier to read.
  
\subsection{RSS Hyperlinks}

This year, we would like to use the ability of PDF viewers to interpret
hyperlinks, specifically to allow each reference in the bibliography to be a
link to an online version of the reference. 
As an example, if you were to cite ``Passive Dynamic Walking''
\cite{McGeer01041990}, the entry in the bibtex would read:

{\small
\begin{verbatim}
@article{McGeer01041990,
  author = {McGeer, Tad}, 
  title = {\href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic Walking}}, 
  volume = {9}, 
  number = {2}, 
  pages = {62-82}, 
  year = {1990}, 
  doi = {10.1177/027836499000900206}, 
  URL = {http://ijr.sagepub.com/content/9/2/62.abstract}, 
  eprint = {http://ijr.sagepub.com/content/9/2/62.full.pdf+html}, 
  journal = {The International Journal of Robotics Research}
}
\end{verbatim}
}
\noindent
and the entry in the compiled PDF would look like:

\def\tmplabel#1{[#1]}

\begin{enumerate}
\item[\tmplabel{1}] Tad McGeer. \href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic
Walking}. {\em The International Journal of Robotics Research}, 9(2):62--82,
1990.
\end{enumerate}
%
where the title of the article is a link that takes you to the article on IJRR's website. 


Linking cited articles will not always be possible, especially for
older articles. There are also often several versions of papers
online: authors are free to decide what to use as the link destination
yet we strongly encourage to link to archival or publisher sites
(such as IEEE Xplore or Sage Journals).  We encourage all authors to use this feature to
the extent possible.

\section{Conclusion} 
\label{sec:conclusion}

The conclusion goes here.

\section*{Acknowledgments}

%% Use plainnat to work nicely with natbib. 

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}


